### 2020-09-01 benchmarking/benchmarkingVM/ESS_round3.tex
complete draft

% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:26:53
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
	(474.88,173.19);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,246.09) --
	( 54.10,233.67);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 54.10,239.88) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,249.96) --
	( 60.20,218.26);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 60.20,234.11) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,226.82) --
	( 66.29,207.10);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 66.29,216.96) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,210.32) --
	( 72.39,191.80);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 72.39,201.06) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,205.70) --
	( 78.49,138.28);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 78.49,171.99) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,250.06) --
	( 84.59,239.46);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 84.59,244.76) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,223.96) --
	( 90.69,209.76);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 90.69,216.86) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,229.79) --
	( 96.79,207.30);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 96.79,218.55) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,218.87) --
	(102.88,218.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {18\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
	(108.98,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,231.18) --
	(115.08,216.59);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (115.08,223.89) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,210.48) --
	(121.18,196.00);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (121.18,203.24) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,217.85) --
	(127.28,208.48);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (127.28,213.17) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,206.09) --
	(133.38,189.08);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (133.38,197.58) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,184.21) --
	(139.47,163.53);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (139.47,173.87) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,274.87) --
	(145.57,264.59);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (145.57,269.73) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,345.05) --
	(151.67,220.65);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (151.67,282.85) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,222.89) --
	(157.77,199.51);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (157.77,211.20) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,224.11) --
	(163.87,224.11);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {20\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
	(169.97,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,237.79) --
	(176.06,235.79);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (176.06,236.79) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,213.87) --
	(182.16,210.98);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (182.16,212.42) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,213.40) --
	(188.26,210.38);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (188.26,211.89) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,192.72) --
	(194.36,185.58);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (194.36,189.15) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,187.16) --
	(200.46,185.57);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (200.46,186.36) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,240.68) --
	(206.56,238.19);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (206.56,239.44) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,223.05) --
	(212.65,219.07);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (212.65,221.06) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,215.97) --
	(218.75,213.85);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (218.75,214.91) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,214.59) --
	(224.85,214.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {16\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
	(230.95,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,250.44) --
	(237.05,241.85);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (237.05,246.14) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,239.13) --
	(243.15,208.60);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (243.15,223.86) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,213.14) --
	(249.24,198.87);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (249.24,206.01) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,219.07) --
	(255.34,189.90);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (255.34,204.48) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,175.34) --
	(261.44,160.05);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (261.44,167.69) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,231.48) --
	(267.54,205.22);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (267.54,218.35) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,253.96) --
	(273.64,239.75);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (273.64,246.86) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,236.72) --
	(279.74,225.81);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (279.74,231.26) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,219.11) --
	(285.83,219.11);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {18\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
	(291.93,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,240.03) --
	(298.03,230.01);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (298.03,235.02) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,238.59) --
	(304.13,208.20);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (304.13,223.39) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,210.81) --
	(310.23,195.70);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (310.23,203.25) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,228.88) --
	(316.33,202.54);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (316.33,215.71) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,175.84) --
	(322.42,163.67);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (322.42,169.76) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,230.74) --
	(328.52,204.43);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (328.52,217.58) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,232.28) --
	(334.62,208.40);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (334.62,220.34) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,233.20) --
	(340.72,221.37);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (340.72,227.29) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,214.66) --
	(346.82,214.66);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {16\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
	(352.92,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,237.99) --
	(359.01,223.51);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (359.01,230.75) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,244.31) --
	(365.11,211.56);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (365.11,227.93) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,216.84) --
	(371.21,196.62);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (371.21,206.73) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,225.85) --
	(377.31,198.06);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (377.31,211.95) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,197.62) --
	(383.41,172.56);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (383.41,185.09) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.51,237.58) --
	(389.51,211.29);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (389.51,224.44) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:30:15
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
	(476.29,173.19);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.56,210.61) --
	( 53.56,170.08);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 53.56,190.34) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.12,246.09) --
	( 59.12,233.67);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 59.12,239.88) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.69,249.96) --
	( 64.69,218.26);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 64.69,234.11) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.25,226.82) --
	( 70.25,207.10);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 70.25,216.96) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.81,209.65) --
	( 75.81,192.67);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 75.81,201.16) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.37,205.70) --
	( 81.37,138.28);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 81.37,171.99) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.94,250.06) --
	( 86.94,239.46);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 86.94,244.76) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.50,223.96) --
	( 92.50,209.76);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 92.50,216.86) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.06,229.79) --
	( 98.06,207.30);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] ( 98.06,218.55) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 53.56,215.85) --
	(103.62,215.85);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.59,284.14) {17\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (109.18,  0.00) --
	(109.18,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.75,234.94) --
	(114.75,216.63);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (114.75,225.78) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.31,231.18) --
	(120.31,216.59);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (120.31,223.89) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.87,210.48) --
	(125.87,196.00);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (125.87,203.24) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.43,217.85) --
	(131.43,208.48);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (131.43,213.17) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.00,207.88) --
	(137.00,192.85);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (137.00,200.36) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.56,184.21) --
	(142.56,163.53);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (142.56,173.87) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.12,274.87) --
	(148.12,264.59);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (148.12,269.73) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.68,345.05) --
	(153.68,220.65);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (153.68,282.85) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.24,222.89) --
	(159.24,199.51);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (159.24,211.20) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (114.75,224.57) --
	(164.81,224.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.78,284.14) {20\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (170.37,  0.00) --
	(170.37,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.93,201.00) --
	(175.93,192.97);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (175.93,196.98) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.49,237.79) --
	(181.49,235.79);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (181.49,236.79) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.05,213.87) --
	(187.05,210.98);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (187.05,212.42) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.62,213.40) --
	(192.62,210.38);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (192.62,211.89) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.18,192.27) --
	(198.18,187.06);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (198.18,189.67) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.74,187.16) --
	(203.74,185.57);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (203.74,186.36) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.30,240.68) --
	(209.30,238.19);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (209.30,239.44) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.87,223.05) --
	(214.87,219.07);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (214.87,221.06) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.43,215.97) --
	(220.43,213.85);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (220.43,214.91) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (175.93,212.74) --
	(225.99,212.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.96,284.14) {15\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (231.55,  0.00) --
	(231.55,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.11,198.51) --
	(237.11,180.05);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (237.11,189.28) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.68,250.44) --
	(242.68,241.85);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (242.68,246.14) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.24,239.13) --
	(248.24,208.60);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (248.24,223.86) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.80,213.14) --
	(253.80,198.87);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (253.80,206.01) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.36,215.64) --
	(259.36,185.82);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (259.36,200.73) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.93,175.34) --
	(264.93,160.05);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (264.93,167.69) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (270.49,231.48) --
	(270.49,205.22);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (270.49,218.35) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.05,253.96) --
	(276.05,239.75);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (276.05,246.86) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.61,236.72) --
	(281.61,225.81);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (281.61,231.26) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.11,215.55) --
	(287.17,215.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (262.14,284.14) {16\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (292.74,  0.00) --
	(292.74,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.30,199.13) --
	(298.30,180.61);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (298.30,189.87) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.86,240.03) --
	(303.86,230.01);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (303.86,235.02) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (309.42,238.59) --
	(309.42,208.20);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (309.42,223.39) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (314.99,210.81) --
	(314.99,195.70);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (314.99,203.25) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.55,225.30) --
	(320.55,196.46);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (320.55,210.88) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (326.11,175.84) --
	(326.11,163.67);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (326.11,169.76) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.67,230.74) --
	(331.67,204.43);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (331.67,217.58) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.23,232.28) --
	(337.23,208.40);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (337.23,220.34) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.80,233.20) --
	(342.80,221.37);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (342.80,227.29) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.30,211.47) --
	(348.36,211.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (323.33,284.14) {15\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (353.92,  0.00) --
	(353.92,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.48,201.98) --
	(359.48,175.41);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (359.48,188.70) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.05,237.99) --
	(365.05,223.51);
\definecolor{fillColor}{RGB}{253,104,0}
